Musical Ornaments

### 2018-05-13 slides/pnwplse.tex
slides complete

\begin{frame}\frametitle{Outline}
\begin{itemize}
\item A look toward the future
\item Music Tools
\item Equivalences
\item Ornaments
\end{itemize}

@@

@@

\begin{frame}\frametitle{Conclusion}
Goes here.
\end{frame}

>>>>

\begin{frame}\frametitle{Outline}
\begin{itemize}
\item A look toward the future
\item Music Tools
\item Equivalences and Ornaments
\end{itemize}

@@

\begin{frame}\frametitle{Music Tools}
\begin{itemize}
\item Collection of composable tools for synthesis and analysis of music
\item Originally written in Haskell
\item Converted to Agda, using Haskell for MIDI interface
\item Explore programming using dependent types in a circumscribed yet rich domain
\item Use math, including transport of equivalences (from HoTT) and Ornaments
\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Equivalent Representations of Pitch}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{pitch}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{chromatic}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{relpitch}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{octave}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{pitchoctave}
\end{frame}

\begin{frame}\frametitle{Equivalences}
\begin{itemize}
\item Define an equivalence between {\tt Pitch} and {\tt PitchOctave}
\item Using HoTT techniques, automatically lift this equivalence to functions defined using \texttt{Pitch}
\item See \textit{Equivalences for Free!} (Tabareau, Tanter, Sozeau)
\item Challenge: Defining base equivalences. Can this be automated?
\end{itemize}
\end{frame}

\begin{frame}[fragile]\frametitle{Ornaments}
\begin{semiverbatim}
data Music a  = ... 
  |  Modify Control (Music a)

data Control = ...
  |  Phrase [PhraseAttribute]

data PhraseAttribute = ...
  |  Orn Ornament

data Ornament =
  Trill | Mordent | InvMordent | DoubleMordent |
  Turn | TrilledTurn | ShortTrill ...
\end{semiverbatim}
\end{frame}

\begin{frame}\frametitle{Ornaments}
\begin{itemize}
\item Functions on a base {\tt Music} structure can be automatically lifted to operate on {\tt Music} ornamented with additional information
\item See works on Ornaments by McBride, Dagand and others
\item Challenge: Shallow embedding of ornaments in Agda
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Conclusion}
\begin{itemize}
\item Music is a good domain in which to explore  practical application of dependent types
\item Using math can be more work at first, but should be a big win in the long term
\item Figure out how to minimize the work and maximize the reward
\end{itemize}
\end{frame}
